An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet Signatures

### 2021-05-27 CMPSpaper_writing/CMPSpaper_writing.Rmd
signatures added

Note that there are parameters in this algorithm that can be specified by the users to conform the structure of their data, such as the length of basis segments in step 1, the number of peaks identified on each scale level in step 2, and the length of the tolerance zone in both step 2 and 3. In our implementation of the CMPS algorithm we took the original CMPS paper [@cmps] as the reference to determine the default values of these parameters. Additionally, as shown in @cmps, using multi segment lengths strategy reduces the number of "false positive" peaks in the cross-correlation curves, thus providing a more conservative way of identifying candidate positions. The main function that combines all steps in the CMPS algorithm described above is called `extract_feature_cmps(...)`. Default values and some explanations of its parameters are as following:

@@

\wj{the followings are revised}
* `x` and `y` are the two bullet signatures. Usually we take `x` as the reference signature (that will be divided into basis segments) and `y` as the comparison signature;
* `seg_length` specifies the length of basis segments [(in mm?)] mentioned in algorithm step 1; 
* `Tx` determines the size of the tolerance zone mentioned in both step 2 and 3;
* `npeaks.set` is a (vector of) integer value(s). This parameter determines which strategy to use to generate candidate positions and the number of peaks to be identified;
* `include` determines the output of the function. Besides the `CMPS.score`, many details of the comparison might be used to understand how the `CMPS.score` is computed. By default, `include = NULL` and the function output will only contain the `CMPS.score`; `include` can also be (an abbreviation of) one of or a vector of the following strings: `"nseg", "congruent.pos", "congruent.seg.idx", "segments", "parameters"`, and `"full_result"`. if `"full_result"` (or its abbreviation) is specified, the ouput will include everything listed below.
  - `nseg`: the number of basis segments we get from the reference signature; this is also the highest possible CMPS score of the comparison;
  - `congruent.pos`: the congruent registration position;
  - `congruent.seg.idx`: the indices of all congruent matching profile segments;
  - `ccp.list`: a list showing identified candidate positions of all basis segments; 
  - `pos.df`: a data frame containing all candidate positions and the number of votes they received;
  - `segments`: a list containing all basis segments;
  - `parameters`: a list containing all input arguments of `extract_feature_cmps`;

@@

@@

>>>>

Note that there are \hh{several} parameters in the CMPS algorithm \hh{that are left to} the users \hh{to decide}, such as the length of basis segments `seg_length` in step 1, the number of peaks `npeaks.set` identified on each scale level in step 2, and the length of the tolerance zone `Tx` in both step 2 and 3. 
In our implementation of the CMPS algorithm we used the parameters given in the original CMPS paper [@cmps] as the default values for these parameters. \hh{XXX However, the authors state that no cross-validation has been done - there might be also issues with respect to resolution of the scans. Further research is needed, until then users are advised to think of default values as starting values and consider alternatives}
<!--Additionally, as shown in @cmps, using multi segment lengths strategy reduces the number of "false positive" peaks in the cross-correlation curves, thus providing a more conservative way of identifying candidate positions.-->
The main function that combines all steps in the CMPS algorithm described above is called `extract_feature_cmps(...)`. Default values and some explanations of its parameters are as following:

@@

\wj{the followings are revised} \hh{XXX this section feels a bit repetitive}
* `x` and `y` are the two bullet signatures. Usually we take `x` as the reference signature (that will be divided into basis segments) and `y` as the comparison signature;
* `seg_length` specifies the length of basis segments [(in mm?)] mentioned in algorithm step 1; 
* `Tx` determines the size of the tolerance zone mentioned in both step 2 and 3;
* `npeaks.set` is a (vector of) integer value(s). This parameter determines which strategy to use to generate candidate positions and the number of peaks to be identified;
* `include` determines the output of the function. Besides the `CMPS.score`, many details of the comparison might be used to understand how the `CMPS.score` is computed. By default, `include = NULL` and the function output will only contain the `CMPS.score`; `include` can also be (an abbreviation of) one of or a vector of the following strings: `"nseg", "congruent.pos", "congruent.seg.idx", "segments", "parameters"`, and `"full_result"`. if `"full_result"` (or its abbreviation) is specified, the ouput will include everything listed below.
  - `nseg`: the number of basis segments we get from the reference signature; this is also the highest possible CMPS score of the comparison;
  - `congruent.pos`: the congruent registration position;
  - `congruent.seg.idx`: the indices of all congruent matching profile segments;
  - `ccp.list`: a list showing identified candidate positions of all basis segments; 
  - `pos.df`: a data frame containing all candidate positions and the number of votes they received;
  - `segments`: a list containing all basis segments;
  - `parameters`: a list containing all input arguments of `extract_feature_cmps`;

@@

\hh{XXX you need a bit of an overview here on the structure of what is coming next: in the remainder of the paper we showcase the use of the CMPS functionality on some examples ...}

@@

\hh{XXX include some signatures here.}

```{r echo=FALSE}
signatures <- bullets %>% unnest(sigs)
signatures %>% ggplot(aes(x = x/1000, y = sig)) + geom_line() + facet_wrap(~bulletland, ncol=6) +
  theme_bw() +
  xlab("Length in mm") +
  ylab("Relative height in micron")
```
